### 2020-03-31 reviews/SIGBOVIK_2020_review_18.tex
Add a special-purpose review

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{\textless mcoblenz@andrew.cmu.edu\textgreater}
\rating{\textless sigbovik@gmail.com\textgreater}
\confidence{Re: SIGBOVIK 2020 Call for Papers and Reviews 2: Total Recall}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{37}
\papertitle{The Pacman effect and the Disc-Sphere Duality}

@@

%%% Replace the following text with your review.
I’m afraid I must object to triple-blind review on the grounds that it, too, may be biased because the
reviewers still know they are reviewers. Have you considered quadruple-blind review, in which reviews are
elicited from reviewers without informing them that they are writing reviews?

>>>>

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{\textless ix@tchow.com\textgreater}
\rating{\textless sigbovik@gmail.com\textgreater}
\confidence{Re: Draft 2020 proceedings!}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{Review of Paper 31}
\papertitle{The SIGBOVIK 2020 field guide to plants}

@@

%%% Replace the following text with your review.
I think the review currently for the guide to plants should probably be attributed to the originator of the couplet (Edward Lear) rather than to "Prof. James McCann" -- I'm not sure there's much joke added (since it ended up on a paper referencing me) and I'm not really comfortable with something I didn't write being attributed to me.

-{}-Jim
